\begin{thebibliography}{99}

 \bibitem[BeHG87]{BeHG87} Bernstein, P., Hadzilacos, V., Goodman, N. \emph{Concurrency Control and Recovery in Database Systems}, 1987.

 \bibitem[BGLL99]{BGLL99} Bernstein, Arthur J., Gerstl, David S., Lewis, Philip M., Lu, Shiyong \emph{Using Transaction Semantics to Increase Performance}, 1999.

 \bibitem[FCEN]{FCEN} Facultad de Ciencias Exactas y Naturales (Universidad de Buenos Aires) \emph{http://www.fcen.uba.ar}

 \bibitem[FCENBD]{FCENBD} `Fundamentals of Databases' Course \\ \emph{http://www-2.dc.uba.ar/materias/bd}

 \bibitem[FCENDC]{FCENDC} Department of Computer Sciences \emph{http://www.dc.uba.ar}

 \bibitem[Fran92]{Fran92} Franklin, Michael J. \emph{Concurrency Control and Recovery}, 1992.

 \bibitem[GHJV95]{GHJV95} Gamma, E., Helm, R., Johnson, R.,Vlissides, J. \emph{Design Patterns, Elements of Reusable Object-Oriented Software}, 1995.

 \bibitem[LBCP07a]{LBCP07a} Leggieri, L., Berlin, J., Cabás, V., Pippia, F. \\ \emph{KANON DBMS Operations manual}, 2007.

 \bibitem[LBCP07b]{LBCP07b} Leggieri, L., Berlin, J., Cabás, V., Pippia, F. \\ \emph{KANON DBMS Technical Report}, 2007.

 \bibitem[MHLPS89]{MHLPS89} Mohan, C., Haderle, D., Lindsay, B., Pirahesh, H., Schwarz, P. \emph{ARIES: A Transaction Recovery Method Supporting Fine-Granularity Locking and Partial Rollbacks Using Write-Ahead Logging}, 1989.

 \bibitem[Moha90]{Moha90} Mohan, C. \emph{ARIES/KVL A Key-Value Locking Method for Concurrency Control of Multiaction Transactions Operating on B-Tree Indexes}, 1990.

 \bibitem[Moha93]{Moha93} Mohan, C. \emph{ARIES/LHS: A Concurrency Control and
Recovery Method Using Write-Ahead Logging for Linear Hashing with Separators}, 1993.

 \bibitem[Moha99]{Moha99} Mohan, C. \emph{Repeating History Beyond ARIES}, 1999.

 \bibitem[MoLe92]{MoLe92} Mohan, C., Levine, F. \emph{ARIES/IM: An Efficient and
High Concurrency Index Management Method Using Write-Ahead Logging}, 1992.

 \bibitem[RaGh03]{RaGh03} Ramakrishnan, R., Gherke, J. \emph{Database Management Systems, 3rd Ed.}, 2003.

 \bibitem[RoMo89]{RoMo89} Rothernlel, K., Mohan, C. \emph{ARIES/NT: A Recovery Method Based on Write-Ahead Logging for Nested Transactions}, 1989.

 \bibitem[Ullm88]{Ullm88} Ullman, J. \emph{Principles of Database and Knowledge Base Systems}, 1988.

 \bibitem[WIISLE]{WIISLE} Isolation Levels \\ \emph{http://en.wikipedia.org/wiki/Isolation\_(computer\_science)}

 \bibitem[WIR2PL]{WIR2PL} Rigurous Two-Phase Locking\\ \emph{http://en.wikipedia.org/wiki/Rigorous\_two-phase\_locking}

 \bibitem[WIS2PL]{WIS2PL} Strict Two-Phase Locking\\ \emph{http://en.wikipedia.org/wiki/Strict\_two-phase\_locking}

 \bibitem[WISHAP]{WISHAP} Shadow Paging \emph{http://en.wikipedia.org/wiki/Shadow\_paging}

 \bibitem[WIWALO]{WIWALO} Write-Ahead Logging \\ \emph{http://en.wikipedia.org/wiki/Write\_ahead\_logging}
 
\end{thebibliography}
